\begin{招待講演}{1}

\bibitem{01早川智彦01}
Tomohiko Hayakawa:  User Performance based on the Effects of Low Video Latency between Visual and Haptic Information in Immersive Environments (Invited), The 6th International Conference on Intelligent Robotics and Control Engineering (IRCE 2023), 2023.8

\bibitem{01早川智彦02}
Tomohiko Hayakawa:  Optical axis control methods for infrastructure inspection, 2nd Intl. Conference Advances in 3OM , OPT23-42,Timisoara, 2023.12


\bibitem{02末石智大01}
末石智大: 高速光学系制御による動的イメージングシステムとその応用, 高速度イメージングとフォトニクスに関する総合シンポジウム2023, 近畿大学, 大阪, 2023.12


\bibitem{hanai-simpo}
華井雅俊、
"ARIM-mdxデータシステム",
ARIM「第２回革新的なエネルギー変換を可能とするマテリアル領域」シンポジウム,
2024年1月

\bibitem{hanai-utac}
華井雅俊,
"ARIM-mdxデータシステム: 材料実験データの利活用に向けた実験施設のDX化", 
第一回UDAC-SRIS合同勉強会,
2023年12月

\bibitem{hanai-gizyutsu}
華井雅俊、
"ARIM-mdxデータシステム"
ARIM 第1回計測技術スタッフ全体研修会,
2023年12月

\bibitem{kawamura_yitp}
河村光晶,
``超伝導密度汎関数理論の精度検証と応用'',
超伝導研究の発展と広がり,
京都大学基礎物理学研究所,
2023年12月.
\bibitem{ykuga45871732}
空閑洋平, データセンタハードウェアへのソフトウェア脆弱試験の適応, Society 5.0時代の安心・安全・信頼を支える基盤ソフトウェア技術の構築, 2024年3月.


\bibitem{ireneli-1}
Irene Li, A Journey from Transformers to Large Language Models: an Educational Perspective, 2023 the 1st International Conference on AI-generated Content (AIGC2023), Aug, 2023


\end{招待講演}

\begin{招待論文}{1}

\bibitem{kawamura_kotai}
吉見一慶, 本山裕一, 青山龍美, 川島直輝, 河村光晶,
物性研の計算物性科学コミュニティ支援活動,
固体物理 Vol. 58, No. 9, 29 (2023).
\bibitem{ykuga45871752}
河原大輔, 空閑洋平, 黒橋禎夫, 鈴木潤, 宮尾祐介, LLM-jp: 日本語に強い大規模言語モデルの研究開発を行う組織横断プロジェクト, 自然言語処理, 31, 1, pp266-279, 2024年.

\end{招待論文}

\begin{受賞}{1}

\bibitem{02末石智大02}
Himari Tochioka, Tomohiro Sueishi, and Masatoshi Ishikawa: SICE Annual Conference International Award, SICE Annual Conference 2023,2023.9

\bibitem{02末石智大03}
田畑智志，末石智大，宮下令央，石川正俊: 2023年 計測自動制御学会 システムインテグレーション部門SI2023 優秀講演賞,第24回計測自動制御学会システムインテグレーション部門講演会 (SI2023), 新潟，2023.12

\bibitem{kawamura_hpci1}
HPCIソフトウェア賞【普及部門賞】最優秀賞, 
「計算物質科学ソフトウェア普及活動」, 
MateriAppsチーム (井戸 康太、福田 将大、笠松 秀輔、三澤 貴宏) および PASUMSチーム (本山 裕一, 河村 光晶, 吉見 一慶), 2
023年5月.

\bibitem{kawamura_hpci2}
HPCIソフトウェア賞【開発部門賞】最優秀賞,
「mVMC」, 
mVMC開発チーム (井戸 康太, 森田 悟史, 吉見 一慶, 本山 裕一, 加藤 岳生, 河村 光晶, Ruquing Xu, 今田 正俊, 三澤 貴宏), 
2023年5月.

\bibitem{kawamura_hpci3}
HPCIソフトウェア賞【開発部門賞】優秀賞, 
「$\mathcal{H}\Phi$」, 
$\mathcal{H}\Phi$開発チーム (河村 光晶, 吉見 一慶, 三澤 貴宏, 井戸 康太, 本山 裕一, 山地 洋平), 
2023年5月.
\bibitem{ykuga43010880}
空閑洋平, 山下記念研究賞, 情報処理学会（OS研究会）, 2024年3月.

\bibitem{ykuga43010877}
空閑洋平, 山下記念研究賞, 情報処理学会（IOT研究会）, 2024年3月.

\bibitem{ykuga43010874}
空閑洋平, 中村遼, 藤村記念ベストプラクティス賞, 情報処理学会（IOT研究会）, 2023年7月.

\bibitem{ykuga9999}
中村遼, 空閑洋平, 明石邦夫, Most Innovative for HPC Uses Award, Data Mover Challenge 2023, 2024年2月.


\bibitem{ireneli-2}
Boming Yang, Dairui Liu, Toyotaro Suzumura, Ruihai Dong and Irene Li,\lq\lq Going Beyond Local: Global Graph-Enhanced Personalized News Recommendations", Proceedings of the 17th ACM Conference on Recommender Systems  (RecSys 2023), 2023 (Best Student Paper Award)

\end{受賞}

\begin{著書}{1}

\end{著書}

\begin{雑誌論文}{1}

\bibitem{kawamura_la2ios2}
H. Ishikawa, T. Yajima, D. Nishio-Hamane, S. Imajo, K. Kindo, and M. Kawamura,
``Superconductivity at 12 K in ${\mathrm{La}}_{2}{\mathrm{IOs}}_{2}$: A $5d$ metal with osmium honeycomb layer'',
Physical Review Materials \textbf{7}, 054804 (2023).

\bibitem{kawamura_hphi}
K. Ido, M. Kawamura, Y. Motoyama, K. Yoshimi, Y. Yamaji, S. Todo, N. Kawashima, T. Misawa,
``Update of $\mathcal{H}\Phi$: Newly added functions and methods in versions 2 and 3'',
Computer Physics Communications \textbf{298}, 109093 (2024).

\bibitem{kawamura_mos2}
F. Ozaki, Dr. S. Tanaka, Y. Choi, W. Osada, K. Mukai, M. Kawamura, M. Fukuda, M. Horio, T. Koitaya, S. Yamamoto, I. Matsuda, T. Ozaki, and J. Yoshinobu,
``Hydrogen-induced Sulfur Vacancies on the $\mathrm{MoS}_2$ Basal Plane Studied by Ambient Pressure XPS and DFT Calculations'',
ChemPhysChem e202300477 (2023).

\bibitem{kawamura_max}
M. Khazaei, S. Bae, R. Khaledialidusti, A. Ranjbar, H. Komsa, S. Khazaei, M. Bagheri, V. Wang, Y. Mochizuki, M. Kawamura, G. Cuniberti, S. M. V. Allaei, K. Ohno, H. Hosono, and H. Raebiger, 
``Superlattice MAX Phases with A-Layers Reconstructed into 0D-Clusters, 1D-Chains, and 2D-Lattices'',
The Journal of Physical Chemistry C \textbf{127}, 30, 14906 (2023).

 \bibitem{kobayashi1-1}
 Wenjing Li, Xiaodan Shi, Dou Huang, Xudong Shen, Jinyu Chen, Hill Hiroki Kobayashi, Haoran Zhang, Xuan Song, Ryosuke Shibasaki,  "PredLife: Predicting Fine-Grained Future Activity Patterns ", IEEE Transactions on Big Data 9(6) 1658-1669.

 \bibitem{kobayashi1-2}
 Wenjing Li, Haoran Zhang, Jinyu Chen, Peiran Li, Yuhao Yao, Xiaodan Shi, Mariko Shibasaki, Hill Hiroki Kobayashi, Xuan Song 0001, Ryosuke Shibasaki,  "Metagraph-Based Life Pattern Clustering With Big Human Mobility Data", IEEE Trans. Big Data 9(1) 227-240.
 
\bibitem{ykuga45871761}
空閑洋平, 中村遼, 遠隔会議システムの計測データを用いたネットワーク品質計測, 情報処理学会論文誌, 65, 3, pp646-655, 2024年3月.

\bibitem{dmiya1}
Masayuki Jimichi, Yoshinori Kawasaki, Daisuke Miyamoto, Chika Saka, Shuichi Nagata,
"Double-Log Modeling of Financial Data with Skew-Symmetric Error Distributions from Viewpoints of Exploratory Data Analysis and Reproducible Research",
Symmetry, MPDI, 15(9), 19 pages, September 2023. 

\bibitem{dmiya2}
Shun Yonamine, Yuzo Taenaka, Youki Kadobayashi, Daisuke Miyamoto,
"Design and implementation of a sandbox for facilitating and automating IoT malware analysis with techniques to elicit malicious behavior: case studies of functionalities for dissecting IoT malware",
Journal of Computer Virology and Hacking Techniques, Springer, 19(2), pp.149-163, March 2023.

\end{雑誌論文}

\begin{査読付}{1}


\bibitem{01早川智彦03}
Yushi Moko, Yuka Hiruma, Tomohiko Hayakawak, Yuriko Ezaki, Yoshimasa Onishi, Masatoshi Ishikawa:A method for calculating crack width using chalking marks in low-contrast 2D images acquired during high-speed driving, In Proc. Of SPIE 12952, 4,2024.3

\bibitem{01早川智彦04}
Tomohiko Hayakawak, Yuka Hiruma, Ke Yushan, Masatoshi Ishikawa
Label-free position tracking in stuffed sparrow using phosphorescence, Conf. on Label-free Biomedical Imaging and Sensing (LBIS) 2024, SPIE Photonics West BiOS, San Francisco，2024.1

\bibitem{01早川智彦05}
Yuki Kubota, Tomohiko Hayakawa, and Masatoshi Ishikawa: Visual Search Tasks under Spatio-Temporal Control Synchronized with Eye Movements, In Proceedings of the 2023 Symposium on Eye Tracking Research and Applications (ETRA '23), Association for Computing Machinery, Article 43, pp.1-2,New York, USA, 2023.6

\bibitem{01早川智彦06}
Yushi Moko, Yuka Hiruma, Tomohiko Hayakawak, Yoshimasa Onishi, Masatoshi Ishikawa:  High-Speed Localization Estimation Method Using Lighting Recognition in Tunnels, 2023 7th International Conference on Intelligent Traffic and Transportation(ICITT 2023) , ML755,Madrid，2023.9

\bibitem{01早川智彦07}
Tomohiko Hayakawa, Yuka Hiruma, Yushan Ke, Masatoshi Ishikawa: Active thermal marker using thermal images of heated areas with visible semiconductor laser, the 10th edition of the International Conference on Optical and Photonic Engineering(icOPEN 2023), 15617, Singapore, 2023.11

\bibitem{02末石智大04}
Himari Tochioka, Tomohiro Sueishi, and Masatoshi Ishikawa: Bounce Mark Visualization System for Ball Sports Judgement Using High-Speed Drop Location Prediction and Preceding Mirror Control, SICE Annual Conference 2023 (SICE2023),2023.9

\bibitem{02末石智大05}
横山恵子，井上満晶，末石智大，谷内田尚司，石川正俊: 非接触・非拘束型の眼球撮影装置を用いた眼球微細運動検知システム, ビジョン技術の実利用ワークショップ (ViEW2023), pp.413-418, IS3-8,横浜,2023.12


\bibitem{hanai-UCC}
Masatoshi Hanai, Mitsuaki Kawamura, Ryo Ishikawa, Toyotaro Suzumura, Kenjiro Taura
"Cloud Data Acquisition from Shared-Use Facilities in A University-Scale Laboratory Information Management System."
In Proceedings of the 16th IEEE/ACM International Conference on Utility and Cloud Computing (UCC 2023), December 5, 2023, Taormina.

\bibitem{hanai-xiaohang}
Xiaohang Xu, Toyotaro Suzumura, Jiawei Yong, Masatoshi Hanai, Chuang Yang, Hiroki Kanezashi, Renhe Jiang, Shintaro Fukushima, 
"Revisiting Mobility Modeling with Graph: A Graph Transformer Model for Next Point-of-Interest Recommendation."
In Proceedings of the 31st ACM International Conference on Advances in Geographic Information Systems (SIGSPATIAL ’23). Association for Computing Machinery, New York, NY, USA, Article
94, 1–10.

\bibitem{job-jsai}
脇聡志, 鈴村豊太郎, 金刺宏樹, 華井雅俊, 小林秀. "強化学習によるマッチング数を最大化するジョブ推薦システム." 人工知能学会全国大会論文集 第 37 回 (2023), 一般社団法人 人工知能学会, 2023.

 \bibitem{kobayashi2-1}
 Usman Haider, Muhammad Hanif, Hill Hiroki Kobayashi, Laxmi Kumar Parajuli, Daisuké Shimotoku, Ahmar Rashid, Sonia Safeer, "Bioacoustics Signal Classification Using Hybrid Feature Space with Machine Learning", Proceedings of 15th International Conference on Computer and Automation Engineering(ICCAE), 2023.  

 \bibitem{kobayashi2-2}
 Leo Uesaka, Ambika Prasad Khatiwada, Daisuk\'e Shimotoku, Laxmi Kumar Parajuli, Manish Raj Pandey, Hill Hiroki Kobayashi, "Applications of Bioacoustics Human Interface System for Wildlife Conservation in Nepal", Proceedings of 2023 International Conference on Human-Computer Interaction (HCII 2023), 2023.  

\bibitem{ykuga43404131}
Ryo Nakamura, Yohei Kuga, Multi-threaded scp: Easy and Fast File Transfer over SSH, Practice and Experience in Advanced Research Computing, 2023年7月.


\bibitem{mobgt}
Xiaohang Xu, Toyotaro Suzumura, Jiawei Yong, Masatoshi Hanai, Chuang Yang, Hiroki Kanezashi, Renhe Jiang, and Shintaro Fukushima. 2023. Revisiting Mobility Modeling with Graph: A Graph Transformer Model for Next Point-of-Interest Recommendation. In Proceedings of the 31st ACM International Conference on Advances in Geographic Information Systems (SIGSPATIAL '23). Association for Computing Machinery, New York, NY, USA, Article 94, 1–10.

\bibitem{glory}
Boming Yang, Dairui Liu, Toyotaro Suzumura, Ruihai Dong, and Irene Li. 2023. Going Beyond Local: Global Graph-Enhanced Personalized News Recommendations. In Proceedings of the 17th ACM Conference on Recommender Systems (RecSys '23). Association for Computing Machinery, New York, NY, USA, 24–34.

\bibitem{sigir}
Md Mostafizur Rahman, Daisuke Kikuta, Satyen Abrol, Yu Hirate, Toyotaro Suzumura, Pablo Loyola, Takuma Ebisu and Manoj Kondapaka, "Exploring 360-Degree View of Customers for Lookalike Modeling",  SIGIR'23 (The 46th International ACM
SIGIR Conference on Research and Development in Information
Retrieval) 

\bibitem{kg-kp}
Anson Bastos, Kuldeep Singh, Abhishek Nadgeri, Johannes Hoffart, Toyotaro Suzumura, Manish Singh,
"Can Persistent Homology provide an efficient alternative for Evaluation of Knowledge Graph Completion Methods?"
In proceedings of The Web Conference (WWW), 2023.

\bibitem{job-aaai}
Waki, Satoshi, Toyotaro Suzumura, and Hiroki Kanezashi. "Optimizing Matching Markets with Graph Neural Networks and Reinforcement Learning." In Workshop on Recommendation Ecosystems: Modeling, Optimization and Incentive Design, AAAI 2024.

\bibitem{num-aaai}
Putra, Refaldi, and Toyotaro Suzumura. "On the Role of Numerical Encoding in Foundation Model of Sequential Recommendation with Sequential Indexing." In Workshop on Recommendation Ecosystems: Modeling, Optimization and Incentive Design. 2024, AAAI 2024


\bibitem{job-jsai}
脇聡志, 鈴村豊太郎, 金刺宏樹, 華井雅俊, 小林秀. "強化学習によるマッチング数を最大化するジョブ推薦システム." 人工知能学会全国大会論文集 第 37 回 (2023), 一般社団法人 人工知能学会, 2023.


\bibitem{ireneli-3}
Irene Li, Thomas George, Alexander Fabbri, Tammy Liao, Benjamin Chen, Rina Kawamura, Richard Zhou, Vanessa Yan, Swapnil Hingmire and Dragomir Radev, \lq\lq A Transfer Learning Pipeline for Educational Resource Discovery with Application in Leading Paragraph Generation", BEA workshop at Association for Computational Linguistics, 2023

\bibitem{ireneli-4}
Irene Li and Boming Yang, \lq\lq NNKGC: Improving Knowledge Graph Completion with Node Neighborhoods", DL4KG Workshop at International Semantic Web Conference, 2023

\bibitem{ireneli-5}
Linxin Song, Jieyu Zhang, Lechao Cheng, Pengyuan Zhou, Tianyi Zhou and Irene Li, \lq\lq NLPBench: Evaluating Large Language Models on Solving NLP Problems", Instruction Workshop at Conference on Neural Information Processing Systems, 2023


\bibitem{ireneli-6}
Linxin Song, Yan Cui, Ao Luo, Freddy Lecue and Irene Li, \lq\lq Better Explain Transformers by Illuminating Important Information", (Findings) The European Chapter of the Association for Computational Linguistics, 2024

\end{査読付}

\begin{公開}{1}


\bibitem{hanai-arim-mdx}
"ARIM-mdxデータシステム",
\url{https://lcnet.t.u-tokyo.ac.jp/data_system/},

\end{公開}

\begin{特許}{1}


\bibitem{hanai-iot}
華井雅俊、河村光晶、石川亮、鈴村豊太郎、
“IoT デバイス、データ転送システムおよびデータ転送方法”,
特願2023-156343,
東大TLOより出願済,
\end{特許}

\begin{発表}{1}


\bibitem{01早川智彦08}
望戸雄史，早川智彦，大西偉允，石川正俊:  トンネル内における照明認識による自己位置推定手法，令和5年度土木学会全国大会第78回学術講演会, CS9-24, 広島, 2023.9

\bibitem{01早川智彦09}
望戸雄史, 蛭間友香, 早川智彦, 柯毓珊, 大西偉允, 石川正俊:  照明認識を利用した高速道路のトンネル外観検査のための自己位置推定手法, 第21回ITSシンポジウム2023, 2-B-13, 富山, 2023.12

\bibitem{02末石智大06}
栃岡陽麻里，末石智大，石川正俊: ボールのバウンド位置予測に基づくダイナミックプロジェクションマッピングの開発， 第28回日本バーチャルリアリティ学会大会 (VRSJ2023), 論文集,3D2-01, 八王子, 2023.9

\bibitem{02末石智大07}
田畑智志，末石智大，宮下令央，石川正俊: 円筒位置姿勢情報の高速フィードバックを用いたダイナミックアナモルフォーシスシステムの開発， 第24回計測自動制御学会システムインテグレーション部門講演会 (SI2023), 講演会論文集, pp.1280-1285, 新潟, 2023.12


\bibitem{dmiya3}
八木 裕輝, 宮本 大輔, 大規模言語モデルを用いたソフトウェア脆弱性の深刻度の推定手法, コンピュータセキュリティシンポジウム, 2023年10月


\bibitem{ireneli-7}
Rui Yang, Haoran Liu, Edison Marrese-Taylor, Qingcheng Zeng, Ke Yuhe, Wanxin Li, Lechao Cheng, Qingyu Chen, James Caverlee, Yutaka Matsuo, Irene Li, \lq\lq KG-Rank: Enhancing Large Language Models for Medical QA with Knowledge Graphs and Ranking Techniques", 2024.

\bibitem{ireneli-8}
Hang Jiang, Xiajie Zhang, Robert Mahari, Daniel Kessler, Eric Ma, Tal August, Irene Li, Alex Pentland, Yoon Kim, Jad Kabbara, Deb Roy, \lq\lq Leveraging Large Language Models for Learning Complex Legal Concepts Through Storytelling", 2024.

\bibitem{ireneli-9}
Rui Yang, Boming Yang, Sixun Ouyang, Tianwei She, Aosong Feng, Yuang Jiang, Freddy Lecue, Jinghui Lu, Irene Li, \lq\lq Leveraging Large Language Models for Concept Graph Recovery and Question Answering in NLP Education", 2024.

\bibitem{ireneli-10}
Rui Yang, Qingcheng Zeng, Keen You, Yujie Qiao, Lucas Huang, Chia-Chun Hsieh, Benjamin Rosand, Jeremy Goldwasser, Amisha D Dave, Tiarnan D.L. Keenan, Emily Y Chew, Dragomir Radev, Zhiyong Lu, Hua Xu, Qingyu Chen, Irene Li,\lq\lq Ascle: A Python Natural Language Processing Toolkit for Medical Text Generation", 2024.

\bibitem{ireneli-11}
Fan Gao, Hang Jiang, Rui Yang, Qingcheng Zeng, Jinghui Lu, Moritz Blum, Dairui Liu, Tianwei She, Yuang Jiang, Irene Li, \lq\lq Evaluating Large Language Models on Wikipedia-Style Survey Generation", 2023.

\bibitem{ireneli-12}
Dairui Liu, Boming Yang, Honghui Du, Derek Greene, Aonghus Lawlor, Ruihai Dong, Irene Li, \lq\lq RecPrompt: A Prompt Tuning Framework for News Recommendation Using Large Language Models", 2023.


\end{発表}

\begin{特記}{1}

\end{特記}

\begin{報道}{1}


\bibitem{ireneli-13}
(Interview) Gemma Conroy, \textit{How ChatGPT and other AI tools could disrupt scientific publishing} \footnote{https://www.nature.com/articles/d41586-023-03144-w}, \textbf{Nature, Featured News}, 10 October 2023 

\end{報道}
