




% % 
% % bibitem を作る
% \begin{雑誌論文}{1}
% \bibitem{feta}
% Bastos, Anson, Abhishek Nadgeri, Kuldeep Singh, Hiroki Kanezashi, Toyotaro Suzumura, and Isaiah Onando Mulang, "How Expressive Are Transformers in Spectral Domain for Graphs?", Transactions on Machine Learning Research (TMLR) ISSN 2835-8856, Journal of Machine Learning Research, 2022.
% \end{雑誌論文}


\begin{査読付}{5}

\bibitem{mobgt}
Xiaohang Xu, Toyotaro Suzumura, Jiawei Yong, Masatoshi Hanai, Chuang Yang, Hiroki Kanezashi, Renhe Jiang, and Shintaro Fukushima. 2023. Revisiting Mobility Modeling with Graph: A Graph Transformer Model for Next Point-of-Interest Recommendation. In Proceedings of the 31st ACM International Conference on Advances in Geographic Information Systems (SIGSPATIAL '23). Association for Computing Machinery, New York, NY, USA, Article 94, 1–10.

\bibitem{glory}
Boming Yang, Dairui Liu, Toyotaro Suzumura, Ruihai Dong, and Irene Li. 2023. Going Beyond Local: Global Graph-Enhanced Personalized News Recommendations. In Proceedings of the 17th ACM Conference on Recommender Systems (RecSys '23). Association for Computing Machinery, New York, NY, USA, 24–34.

\bibitem{sigir}
Md Mostafizur Rahman, Daisuke Kikuta, Satyen Abrol, Yu Hirate, Toyotaro Suzumura, Pablo Loyola, Takuma Ebisu and Manoj Kondapaka, "Exploring 360-Degree View of Customers for Lookalike Modeling",  SIGIR'23 (The 46th International ACM
SIGIR Conference on Research and Development in Information
Retrieval) 

\bibitem{kg-kp}
Anson Bastos, Kuldeep Singh, Abhishek Nadgeri, Johannes Hoffart, Toyotaro Suzumura, Manish Singh,
"Can Persistent Homology provide an efficient alternative for Evaluation of Knowledge Graph Completion Methods?"
In proceedings of The Web Conference (WWW), 2023.

\bibitem{job-aaai}
Waki, Satoshi, Toyotaro Suzumura, and Hiroki Kanezashi. "Optimizing Matching Markets with Graph Neural Networks and Reinforcement Learning." In Workshop on Recommendation Ecosystems: Modeling, Optimization and Incentive Design, AAAI 2024.

\bibitem{num-aaai}
Putra, Refaldi, and Toyotaro Suzumura. "On the Role of Numerical Encoding in Foundation Model of Sequential Recommendation with Sequential Indexing." In Workshop on Recommendation Ecosystems: Modeling, Optimization and Incentive Design. 2024, AAAI 2024


\bibitem{job-jsai}
脇聡志, 鈴村豊太郎, 金刺宏樹, 華井雅俊, 小林秀. "強化学習によるマッチング数を最大化するジョブ推薦システム." 人工知能学会全国大会論文集 第 37 回 (2023), 一般社団法人 人工知能学会, 2023.
\end{査読付}

% \begin{著書}{2}

% \bibitem{fl-book}
% Toyotaro Suzumura, Yi Zhou, Ryo Kawahara, Nathalie Baracaldo, Heiko Ludwig,
% "Federated Learning for Collaborative Financial Crimes Detection",
% Ludwig, H., Baracaldo, N. (eds) Federated Learning. Springer, Cham. https://doi.org/10.1007/978-3-030-96896-0\_20

% \bibitem{jsai-gnn}
% 鈴村 豊太郎, 金刺 宏樹, 華井 雅俊, グラフニューラルネットワークの広がる活用分野, 人工知能, 2023, 38 巻, 2 号, p. 139-148, 公開日 2023/03/02, Online ISSN 2435-8614, Print ISSN 2188-2266, https://doi.org/10.11517/jjsai.38.2\_139

% \end{著書}

% \begin{招待講演}{3}
% \bibitem{fugaku} 鈴村豊太郎「夢の形～未来のコンピュータ～」（パネリスト）、スーパーコンピュータ「富岳」第2回成果創出加速プログラムシンポジウム「富岳百景」、2022年12月21日
% \bibitem{jsse1}鈴村豊太郎,「データ活用社会創成プラットフォームmdxおよび 大規模グラフニューラルネットワーク」, 第34回CCSEワークショップ「原子力材料研究開発におけるDX推進の現状と将来：原子力材料研究開発の革新と新展開」, 2023年2月24日
% \bibitem{jsse2}鈴村豊太郎,「人工知能の最先端研究に迫る ～大規模グラフニューラルネットワークの世界へ」, 東京大学柏キャンパス一般公開2022、特別講演会、2022年10月22日
% \bibitem{rakuten}Toyotaro Suzumura, “How Will Data and AI Change the World?”,  Rakuten Optimism Conference, Tokyo, Japan, September 29, 2022
% \bibitem{rccs}Toyotaro Suzumura,  “Large-Scale Graph Neural Networks for Real-World Industrial Applications”, The 5th R-CCS International Symposium, Kobe Japan, February 7, 2023
% \bibitem{france}Toyotaro Suzumura,  “Large-Scale Graph Neural Networks for Real-World Industrial Applications”, International Workshop “HPC challenges for new extreme scale application” held by French Alternative Energies and Atomic Energy Commission, Paris, France, March 6, 2023
% \bibitem{barcelona}Toyotaro Suzumura,  “Large-Scale Graph Neural Networks for Real-World Industrial Applications”, Barcelona Supercomputing Center, Barcelona, Spain, March 10, 2023
% \end{招待講演}



% \begin{発表}{1}
% \bibitem{sms}
% 脇 聡志, 鈴村 豊太郎, 金刺 宏樹, 小林 秀, "強化学習によるマッチング数を最大化するジョブ推薦システム." 第37回人工知能学会全国大会 (2023),  一般社団法人 人工知能学会, (2023年6月発表予定)

% \end{発表}
