\begin{招待講演}{1}
\bibitem{kawamura_yitp}
河村光晶,
``超伝導密度汎関数理論の精度検証と応用'',
超伝導研究の発展と広がり,
京都大学基礎物理学研究所,
2023年12月.
\end{招待講演}

\begin{招待論文}{1}
\bibitem{kawamura_kotai}
吉見一慶, 本山裕一, 青山龍美, 川島直輝, 河村光晶,
物性研の計算物性科学コミュニティ支援活動,
固体物理 Vol. 58, No. 9, 29 (2023).
\end{招待論文}

\begin{受賞}{1}
\bibitem{kawamura_hpci1}
HPCIソフトウェア賞【普及部門賞】最優秀賞, 
「計算物質科学ソフトウェア普及活動」, 
MateriAppsチーム (井戸 康太、福田 将大、笠松 秀輔、三澤 貴宏) および PASUMSチーム (本山 裕一, 河村 光晶, 吉見 一慶), 2
023年5月.

\bibitem{kawamura_hpci2}
HPCIソフトウェア賞【開発部門賞】最優秀賞,
「mVMC」, 
mVMC開発チーム (井戸 康太, 森田 悟史, 吉見 一慶, 本山 裕一, 加藤 岳生, 河村 光晶, Ruquing Xu, 今田 正俊, 三澤 貴宏), 
2023年5月.

\bibitem{kawamura_hpci3}
HPCIソフトウェア賞【開発部門賞】優秀賞, 
「$\mathcal{H}\Phi$」, 
$\mathcal{H}\Phi$開発チーム (河村 光晶, 吉見 一慶, 三澤 貴宏, 井戸 康太, 本山 裕一, 山地 洋平), 
2023年5月.
\end{受賞}


\begin{雑誌論文}{4}
\bibitem{kawamura_la2ios2}
H. Ishikawa, T. Yajima, D. Nishio-Hamane, S. Imajo, K. Kindo, and M. Kawamura,
``Superconductivity at 12 K in ${\mathrm{La}}_{2}{\mathrm{IOs}}_{2}$: A $5d$ metal with osmium honeycomb layer'',
Physical Review Materials \textbf{7}, 054804 (2023).

\bibitem{kawamura_hphi}
K. Ido, M. Kawamura, Y. Motoyama, K. Yoshimi, Y. Yamaji, S. Todo, N. Kawashima, T. Misawa,
``Update of $\mathcal{H}\Phi$: Newly added functions and methods in versions 2 and 3'',
Computer Physics Communications \textbf{298}, 109093 (2024).

\bibitem{kawamura_mos2}
F. Ozaki, Dr. S. Tanaka, Y. Choi, W. Osada, K. Mukai, M. Kawamura, M. Fukuda, M. Horio, T. Koitaya, S. Yamamoto, I. Matsuda, T. Ozaki, and J. Yoshinobu,
``Hydrogen-induced Sulfur Vacancies on the $\mathrm{MoS}_2$ Basal Plane Studied by Ambient Pressure XPS and DFT Calculations'',
ChemPhysChem e202300477 (2023).

\bibitem{kawamura_max}
M. Khazaei, S. Bae, R. Khaledialidusti, A. Ranjbar, H. Komsa, S. Khazaei, M. Bagheri, V. Wang, Y. Mochizuki, M. Kawamura, G. Cuniberti, S. M. V. Allaei, K. Ohno, H. Hosono, and H. Raebiger, 
``Superlattice MAX Phases with A-Layers Reconstructed into 0D-Clusters, 1D-Chains, and 2D-Lattices'',
The Journal of Physical Chemistry C \textbf{127}, 30, 14906 (2023).

\end{雑誌論文}

